Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2022-03-28 reportTII-ArticleHIL.tex
Added figure to report
Updated Report

 In this section, we illustrate how a neural network can be used to model a
 dynamic system in general. Neural network is a system approximation technique
 that .......
 The main structure of a neural network consists of neurons, input layer of
 neurons, one or more hidden layers, and the output layer of neurons. The
 neurons of the hidden layers and the output layer have processing capabilities.
 The actual structure of a neural network follows parallel and distributed system
 architecture. .....

@@

\subsection{Steering System Modeling}

\subsection{Acceleration System Modeling}

@@

The following are the results of neural network training for the steering system.

>>>>

 In this section, we illustrate how a neural network can be used to model a
 dynamic system in general. Neural network is a system approximation technique
 that utilizes the Universal Approximation Theorem, which states that any neural network architecture
 can find a mathematical function $y=f(x)$ that maps inputs $x$ to outputs $y$. The architecture of the 
 neural network and the complexity of the dataset employed affect the accuracy of the function. This theorem
 shows that there will be a determinable function from some neural network architecture and this theorem holds
 for any number of inputs and outputs. 
 The main structure of a neural network consists of neurons, input layer of
 neurons, one or more hidden layers, and the output layer of neurons. The
 neurons of the hidden layers and the output layer have processing capabilities.
 The actual structure of a neural network follows parallel and distributed system
 architecture.

@@

\subsection{Steering System Modeling}
To develop a model of the steering system, we employed multiple methods. The first method that we tried was generating a NARX model and a transfer function model, making use of the System Identification Toolbox in MATLAB. The NARX model we developed was not accurate and did not track the output of the steering system data. The transfer function model we developed was more reliable tracking the output of the steering system data, but was unable to meet the error requirements, as there were sudden changes that forced high error peaks. Then we employed a neural network model, making use of the Neural Network Time Series Toolbox in MATLAB. With the neural network model, the model was able to reliably and accurately track the output of the steering system data and stayed within the error requirements.

\subsection{Acceleration System Modeling}
To develop a model of the acceleration system, we employed multiple methods. The first method that we tried was generating a NARX model and a transfer function model, making use of the System Identification Toolbox in MATLAB. The NARX model we developed was not accurate and did not track the output of the acceleration system data. The transfer function model we developed was more reliable tracking the output of the acceleration system data, but was unable to meet the error requirements, as there were sudden changes that forced high error peaks. Then we employed a neural network model, making use of the Neural Network Time Series Toolbox in MATLAB. With the neural network model, the model was able to reliably and accurately track the output of the acceleration system data and stayed within the error requirements.

@@

To develop the model of the steering system using a neural network architecture, we used one data subset to train the model and then used an additional subset of data to verify the model worked. The neural network model used a feedforward network that had one hidden layer containing three neurons. 
%The following are the results of neural network training for the steering system.
